---
title: "Chun Su CV"
author: Chun Su
date: "`r Sys.Date()`"
params:
  pdf_mode:
    value: true
output:
  pagedown::html_resume:
    self_contained: true
    css: ['override.css', 'resume', 'https://cdn.jsdelivr.net/gh/jpswalsh/academicons@1/css/academicons.min.css']
---

```{css, echo=FALSE}
.pagedjs_page:not(:first-of-type) {
  --sidebar-width: 0rem;
  --sidebar-background-color: #ffffff;
  --main-width: calc(var(--content-width) - var(--sidebar-width));
  --decorator-horizontal-margin: 0.2in;
}
```

```{r, include=F}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)

library(tidyverse)

source("helper_functions.R")

cv_google_sheet <- "https://docs.google.com/spreadsheets/d/1dcd31plt_SmlHMWiNDiXHgFcJIHdhPyGVORvgCt5EMk/edit?usp=sharing"

cv <- create_cv_obj(cv_google_sheet)
```


# Aside

![Chun Su](https://media-exp1.licdn.com/dms/image/C4E03AQH2-cbjQTrAKw/profile-displayphoto-shrink_800_800/0/1516780179563?e=1667433600&v=beta&t=ycj2c4SfbINkl4kwmciBOz0itQXDqzdxYhCp82HZ0-I)

## Contact Info {#contact}

```{r}
print_contact_info(cv)
```

## Skill Highlights {#skills}

```{r}
print_skills(cv)
```


## Disclaimer {#disclaimer}

Last updated on `r Sys.Date()`.

Prepared by {Pagedown}

# Main

## Chun Su {#title}

### Bioinformatics Scientist \| Computational Biologist

I have 10+ years of hands-on experience in bioinformatics. Skilled in both molecular cloning and computational analysis of next generation sequencing (NGS) data. Proficient in a variety of programming languages, HPC systems, cutting-edge bioinformatic software, and multivariate statistical analysis. Knowledgeable about molecular cell biology and immunology. Proven experience in troubleshooting and meeting challenging deadlines in a fast-paced work environment. Excellent professional communication and leadership skills developed through community service and extensive teaching experiences.

## Education {data-icon=graduation-cap data-concise=true}

```{r}
print_section(cv, "Education")
```


## Professional Experience {data-icon="suitcase"}

```{r}
print_section(cv, "Research Experience")
```

## Leadership Experience {data-icon="black-tie"}

```{r}
print_section(cv, "Leadership Experience")
```

## Awards and Honors {data-icon="trophy"}

```{r}
print_section(cv, "Awards and Honors")
```

## Posters and Presentations {data-icon="users"}

```{r}
print_section(cv, "Poster and Presentation")
```

## Selected Publications {data-icon="book"}

```{r}
print_section(cv, "Publications")
```

